---
title: "DW_3.2"
author: "Luiza Santos"
date: "May 31, 2018"
output: pdf_document
---

## Loading the data

```{r Loading}
library("tidyverse")
titanic <- read_csv('titanic_original.csv')
```

## Port of embarkation

```{r PE}
titanic <- titanic %>%
  mutate(embarked = ifelse(embarked == " ", "S", as.character(embarked)))
```

##Age

```{r Age}
mean(titanic$age, na.rm=TRUE)
titanic <- titanic %>%
  mutate(age = ifelse(is.na(age), "30", as.numeric(age)))
```

##Lifeboat

```{r Lifeboat}
titanic <- titanic %>% 
  mutate(boat = ifelse(is.na(boat) | boat == " ", "None", as.character(boat)))
```

##Cabin

Many passangers don't have a cabin number associated with their records. It seems like cabin records were much more prevalent among people of higher SES. Since there seems to be a relationship between SES and survival rate, the existence/absence of cabin records could be used to indirectly predict survival outcomes. 

```{r cabin}
titanic <- titanic %>%
  mutate(has_cabin_number = ifelse(is.na(cabin), 0, 1))
```

##Save Clean Dataset

```{r save}
write_csv(titanic, 'titanic_clean.csv')
```







