---
title: "Twitter_project_test"
author: "Luiza Santos"
date: "July 13, 2018"
output: html_document
---

## Loading

```{r}
library(rtweet)
library(syuzhet)
library(ggplot2)
library(twitteR)
library(igraph)
library(ggraph)
library(tidyverse)
library(ROAuth)
```

## Authorization keys

I have been having some trouble with this step (I receive an error message and can't seem to get an authorization code).

```{r twitter}
requestURL <- "https://api.twitter.com/oauth/request_token"
accessURL <- "https://api.twitter.com/oauth/access_token"
authURL <- "https://api.twitter.com/oauth/authorize"
consumerKey <- "m6iCVpG57RnEeZJJPIJVYYTxb"
consumerSecret <- "Q7s7WMRtUB4yS8F0Kbx4MgQaKnGIalZOuDgPQkXM2BJnNA2Aor"
my_oauth <- OAuthFactory$new(consumerKey=consumerKey, consumerSecret=consumerSecret, 
                             requestURL=requestURL, accessURL=accessURL, authURL=authURL)

my_oauth$handshake(cainfo = system.file("CurlSSL", "cacert.pem", package = "RCurl"))

```

Interestingly, I found this package in Github that estimates a Twitter user’s political ideology based on the accounts they follow. 

```{r}
install.packages("devtools")
library(devtools)
install_github("pablobarbera/twitter_ideology/pkg/tweetscores")
library(tweetscores)
```

Here is more information on the package: https://github.com/pablobarbera/twitter_ideology

Currently, some U.S. politicians with high Twitter following are: Donald Trump, Hillary Clinton, Barack Obama, Arnold Schwarzenegger, Mitt Romney, Paul Ryan, Joe Biden, John McCain, Bernie Sanders (that would give me 5 Republicans and 5 Democrats)

After plotting their ideology, I would like to run a sentiment analysis of their tweets and detect their moral rhetoric according to the dictionary provided by the Moral Foundations Theory. 

MFT posits that, cross-culturally, all moral concerns are rooted in five general content domains: Care/harm (sensitivity to the suffering of others), Fairness/cheating, (reciprocal social interactions and the motivations to be fair and just when working together), Loyalty/betrayal (promoting ingroup cooperation, sacrifice, and trust), Authority/subversion (endorsing social hierarchy), and Purity/degradation (promoting cleanliness of the body and the soul over hedonism). 

The researchers claim that liberals tend to show greater endorsement and use of the Harm/care and Fairness/reciprocity foundations compared to the other 3 foundations, whereas conservatives endorsed and used the 5 foundations more equally.

Paper with moral dictionary: http://www-bcf.usc.edu/~jessegra/papers/GrahamHaidtNosek.2009.Moral%20foundations%20of%20liberals%20and%20conservatives.JPSP.pdf

My idea was to use these politicians tweets to test this claim, while also trying to see if there are any differences between moderate and more extreme politicians. 

I tried to apply this idea to a dataset I found on Kaggle (https://www.kaggle.com/gsdeepakkumar/presidential-candidate-tweets-an-analysis-with-r/notebook) that has past tweets from Hillary Clinton and Donald Trump. 

I used the following code: 
```{r}
#Open csv

tweets <- read.csv("tweets.csv")

Hillary <- subset(tweets,handle=="HillaryClinton") 

library(stringi)

#Preprocessing

Hillary_text <- stri_trim(Hillary$text) #Strip surrounding whitespace
Hillary_text <- stri_trans_tolower(Hillary$text) #transform to lower case

#Tokenization

install.packages("quanteda")
library(quanteda)
Hillary_tokens <- tokens(Hillary_text)

#Creating a Document Term Matrix
Hillary_dfm <- dfm(Hillary_tokens)

#Moral dictionary
Moral_dict <- dictionary(list(harm = c("safe*", "peace*", "compassion*", "empath*", "sympath*", "care", "caring", "protect*", "shield", "shelter", "amity", "secur*", "benefit*", "defen*", "guard*", "preserve", "harm","suffer*", "war", "wars", "warl*", "warring", "fight","violen*", "hurt*", "kill", "kills", "killer*", "killed", "killing", "endanger*", "cruel*", "brutal*", "abuse*", "damag*", "ruin*", "ravage", "detriment*", "crush*", "attack*", "annihilate*", "destroy", "stomp", "abandon*", "spurn", "impair", "exploit", "exploits", "exploited", "exploiting", "wound"),
                              fairness = c("fair", "fairly", "fairness", "fair*", "fairmind*", "fairplay", "equal*", "justice", "justness", "justifi*", "reciproc*", "impartial*", "egalitar*", "rights", "equity","evenness", "equivalent", "unbias*", "tolerant", "equable", "balance*", "homologous", "unprejudice*","reasonable", "constant", "honest*", "unfair*","unequal*", "bias*", "unjust*", "injust*", "bigot", "discriminat*", "disproportion*","inequitable", "prejud*", "dishonest", "unscrupulous", "dissociate", "preference", "favoritism", "segregat*", "exclusion", "exclud*")))

dict_hillary <- dfm_lookup(Hillary_dfm, Moral_dict, nomatch = "_unmatched")
tail(dict_hillary)


```

I ended up with a dfm that listed all the number of words used per tweet and detected the moral words related to harm and fairness (I will add the other moral foundations when I have more time). 

Now, I would like to add the count of all "harm" words and all "fairness" words to see if I could compare them to the number used by Donald Trump, but I don't know how to do that with a dfm. 

The website I used for reference on quanteda: http://kenbenoit.net/pdfs/text_analysis_in_R.pdf

